Face Attractiveness and the Sense of Reality

### 2022-09-08 analysis.Rmd
update

```{r message=FALSE, warning=FALSE}
dfsub$Cor_Trustworthy <- NA
dfsub$Cor_Attractive <- NA
for (participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "Cor_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "Cor_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
}
```

@@

p_cor <- dfsub |>
  select(Participant, starts_with("Cor")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "Cor_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Correlation", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
  library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size=size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

@@

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, dfsub$Participant)) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

>>>>

```{r message=FALSE, warning=FALSE}
dfsub$r_Trustworthy <- NA
dfsub$r_Attractive <- NA
dfsub$r_Goodlooking <- NA
for (participant in dfsub$Participant) {
  dfsub[dfsub$Participant == participant, "r_Trustworthy"] <- cor(df[df$Participant == participant, "Trustworthy"], df[df$Participant == participant, "Norms_Trustworthy"])
  dfsub[dfsub$Participant == participant, "r_Attractive"] <- cor(df[df$Participant == participant, "Attractive"], df[df$Participant == participant, "Norms_Attractive"])
  dfsub[dfsub$Participant == participant, "r_Goodlooking"] <- cor(df[df$Participant == participant, "Goodlooking"], df[df$Participant == participant, "Norms_Attractive"])
}
```

@@

p_cor <- dfsub |>
  select(Participant, starts_with("r_")) |> 
  pivot_longer(-Participant) |> 
  mutate(name = str_remove(name, "r_")) |> 
  ggplot(aes(x = Participant, y = value)) +
  geom_bar(aes(fill = name), stat = "identity", position = "dodge") +
  scale_y_continuous(expand = c(0, 0)) +
  scale_fill_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  scale_color_manual(values = c("#F44336", "#9C27B0", "#5227b0")) +
  see::theme_modern() +
  theme(axis.text.x = element_text(angle = 45, hjust=1),
        legend.position = "top") +
  labs(y = "Correlation", fill="") +
  guides(color = "none") +
  ggside::geom_ysidedensity(aes(x= after_stat(scaled), color = name)) +
  ggside::theme_ggside_void() +
  ggside::scale_ysidex_continuous(expand = c(0, 0))

@@

plot_waffle <- function(dfsub, what = "Nationality", title = what, rows = 8, size=3) {
  # library(emojifont)
  ggwaffle::waffle_iron(dfsub, what, rows = rows) |>
    # mutate(label = emojifont::fontawesome('fa-smiley')) |>
    # mutate(label = emojifont::emoji('smiley')) |>
    ggplot(aes(x, y)) +
    geom_point(aes(color = group), shape = "square", size=size) +
    # ggwaffle::geom_waffle(color = "white") +
    # geom_point() +
    # geom_text(aes(color=group ,label=label), family='fontawesome-webfont', size=4) +
    # geom_text(aes(color=group ,label=label), family='EmojiOne', size=4) +
    coord_equal() +
    ggtitle(title) +
    labs(fill = "", color = "") +
    # scale_x_continuous(expand = c(0, 0)) +
    # scale_y_continuous(expand = c(0, 0)) +
    theme_void() +
    # ggwaffle::theme_waffle() +
    theme(plot.title = element_text(face = "bold", hjust = 0.5))
}
```

@@

```{r message=FALSE, warning=FALSE}
df |>
  # mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
  #   summarize(Real = mean(Real)) |>
  #   ungroup() |>
  #   arrange(Real) |>
  #   pull(Participant))) |>
  mutate(Participant = fct_relevel(Participant, as.character(dfsub$Participant))) |> 
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9, normalize = "groups") +
  geom_vline(xintercept = 0.5, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(0, 1),
    expand = c(0, 0),
    breaks = c(0, 0.5, 1),
    label = c("Fake", "", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    # axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

#### Effect of Delay
